\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts,amsthm}
%\usepackage{algorithmic}
%\usepackage{algorithm2e}
\usepackage{algpseudocode}                                 % new algorithm package
\usepackage{algorithm}
\usepackage[subrefformat=parens,farskip=0pt,justification=centering]{subfig}
\captionsetup[subfigure]{labelformat=simple}               % avoid "double brackets" in sub-figure caption
\renewcommand\thesubfigure{(\alph{subfigure})}             % "Fig.~1b"-->"Fig.1(b)"
\usepackage[bookmarks=false]{hyperref}
\hypersetup{
    colorlinks = true,
    citecolor  = blue,
    linkcolor  = blue,
    urlcolor   = blue,
}
\usepackage{cleveref}
\Crefformat{figure}{Fig.~#2#1#3}                           % "Fig.", instead of "Figure"
\Crefname{subfigure}{Fig.}{Figs.}
\Crefformat{table}{TABLE~#2#1#3}                           % "TABLE", instead of "Table"
\usepackage{caption}
\captionsetup[table]{skip=4pt}
\usepackage{balance}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{multirow}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
    
\graphicspath{ {./pics/} }
\newcommand{\etal}{\textit{et al}.}

\begin{document}

\title{Supervised-learning Congestion Predictor For Routability-Driven Global Routing\\
}

% \author{\IEEEauthorblockN{1\textsuperscript{st} Given Name Surname}
% \IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
% \textit{name of organization (of Aff.)}\\
% City, Country \\
% email address}
% \and
% \IEEEauthorblockN{2\textsuperscript{nd} Given Name Surname}
% \IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
% \textit{name of organization (of Aff.)}\\
% City, Country \\
% email address}
% \and
% \IEEEauthorblockN{3\textsuperscript{rd} Given Name Surname}
% \IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
% \textit{name of organization (of Aff.)}\\
% City, Country \\
% email address}
% \and
% \IEEEauthorblockN{4\textsuperscript{th} Given Name Surname}
% \IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
% \textit{name of organization (of Aff.)}\\
% City, Country \\
% email address}
% \and
% \IEEEauthorblockN{5\textsuperscript{th} Given Name Surname}
% \IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
% \textit{name of organization (of Aff.)}\\
% City, Country \\
% email address}
% }

\maketitle

\begin{abstract}
    There is on-going development in technology that is pushing the design to an advanced degree of complexity.
    It affects the convergence of physical design, in which routing is one the most critical stages.
    Routability has hit the bottleneck, because congestion estimated by conventional routers does not cope well with modern sophisticated routing parameters, which has an adverse effect on design feasibility.
    Several techniques have recently been developed to predict routability information through a supervised-learning based mechanism.
    However, features extracted by such methods are rather primitive to represent actual physical properties.
    Furthermore, lack of global information led to worse global routing performance.
    In this paper, we propose a supervised-learning regression model which is able to capture accurate global routing behaviours, through which a congestion prediction model is trained to improve the global routing.
    Experimental results show that, in contrast with conventional global-routing-based congestion estimation, our proposed work is at least 9.33$\times$ faster in execution, while maintaining an accurate prediction.
    Moreover, by integrating our model into the router, a better routing topology is achieved, and a superior quality of performance is observed. 
\end{abstract}

\begin{IEEEkeywords}
Back-end design, physical design, placement, routing, routability, supervised data learning
\end{IEEEkeywords}

\input{./doc/Introduction}
\input{./doc/Preliminaries}
\input{./doc/Methodology}
\input{./doc/Result}
\input{./doc/Conclusion}

%\balance
\bibliographystyle{IEEEtran}
\bibliography{./ref/Top,./ref/IEEEabrv}

\end{document}
